04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
replace dds with vsd PCA

hypPCA <- returnPCAs2(dds.hypothalamus)
plotPC12(hypPCA, "Hypothalamus")

pitPCA <- returnPCAs2(dds.pituitary)
plotPC12(pitPCA, "Pituitary")

gonPCA <- returnPCAs2(dds.gonad)
plotPC12(gonPCA, "Gonad")

>>>>

hypPCA <- returnPCAs2(vsd.hyp)
plotPC12(hypPCA, "Hypothalamus")

pitPCA <- returnPCAs2(vsd.pit)
plotPC12(pitPCA, "Pituitary")

gonPCA <- returnPCAs2(vsd.gon)
plotPC12(gonPCA, "Gonad")
